Reproducible Research in R: A tutorial on how to do the same thing more than once

### 2021-09-17 manuscript.Rmd
add multicollinearity example

>>>>

Take the following example: A preregistration intended to include "working memory" and "fluid intelligence" as predictors for reaction time in an experiment but after gathering data both constructs exhibit high collinearity.
The authors decide that for their purpose these variables are interchangable and remove one.
For them this change simply does not effect the core of their theory but was an auxiliary assumption and they might be right.
Another researcher, however, who e.g. hoped to incorporate their results into a theory about intelligence, might disagree about the importance of this assumption.
